Minimal trap-spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-04 cmsb22.tex
Add the full list of models with reference papers

\begin{table}[!ht]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the selected real-world models.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. For each method, Column "\(|M|\)" denotes the number of minimal trap spaces and Column "time (s)" denotes the computation time in seconds.
    "DNF" means that the method did not finish the computation within one hour.}
  \centering
  \label{tab:result_real}
  \begin{tabular}{lrrrrrrr}
    \toprule
    & & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Proposed method}\\
    \cmidrule(lr){5-6}\cmidrule(lr){7-8}
    model & $n$ & $e$ & $s$ & $|M|$ & time (s) & $|M|$ & time (s) \\ \midrule
    cascade-3~\cite{Tsirvouli2020} & 183 & - & 0 & - & - & 1 & 1.65 \\
    CHO-2016 & 200 & - & 13 & - & - & 1024 & 2.10 \\
    colitis-associated-colon-cancer~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 153 & 1 & - & - & 10 & 0.18 \\
    THIL\_17 & 92 & - & 16 & - & - & 5724 & 0.90 \\
    ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 1100 & 22 & DNF & DNF & DNF & DNF \\
    er-stress & 182 & 266 & 75 & - & - & 25600 & 4.54 \\
    Alzheimer~\cite{aghamiri2020automated} & 1169 & - & 469 & - & - & 49152 & 66.17 \\
    cholocystokinin~\cite{aghamiri2020automated} & 404 & - & 95 & - & - & 705024 & 1080.35 \\
    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 557 & 9 & - & - & 375850 & 331.87 \\
    T-cell-check-point & 218 & - & 34 & - & - & 15360 & 4.33 \\
    HIV-1-with-T-cell-signaling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & DNF & DNF & 1408 & 1.44 \\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & - & - & 5120 & 0.99 \\
    human-network & 1953 & - & 675 & DNF & DNF & 2048 & 1770.98 \\
    IL-6-signalling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 86 & 149 & 15 & - & - & 512 & 0.32 \\
    immune-system & 164 & 506 & 13 & DNF & DNF & 36852 & 14.19 \\
    inflammatory-bowel-disease~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 287 & 0 & DNF & DNF & 1 & 296.23 \\
    influenza-virus-replication-cycle~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & - & - & 2560 & 1.07 \\
    interferon-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & - & - & 512 & 0.43 \\
    KORKUT-2015 & 99 & - & 12 & DNF & DNF & 2060 & 2.86 \\
    KY-PA & 150 & 304 & 72 & - & - & 512 & 3.79 \\
    RA-apoptosis~\cite{aghamiri2020automated} & 431 & - & 59 & DNF & DNF & 640 & 0.70 \\
    CELL CYCLE 2020 & 121 & 493 & - & - & - & 78 & 3.72 \\
    S1\_Table & 1659 & - & 522 & DNF & DNF & 1024 & 1511.07 \\
    signaling-in-macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 533 & 19 & - & - & 512 & 1.58 \\
    SIPC~\cite{Montagud2021} & 133 & 431 & 0 & - & - & 812 & 1.40 \\
    SPBP & 66 & 139 & 13 & - & - & 512 & 0.17 \\
    SN5~\cite{kim2013rmod} & 2746 & - & 835 & DNF & DNF & 2048 & 3094.04 \\
    TCR-TLR5-signaling-2018 & 130 & 273 & 2 & - & - & 48 & 0.50 \\
    T-LGL-survival-network-2008~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 61 & 193 & 7 & - & - & 318 & 0.24 \\
    TUREI-2016 & 4691 & - & 1257 & DNF & DNF & DNF & DNF \\
    VIRUS-RE-CYC & 154 & 268 & 25 & - & - & 1024 & 0.67 \\ \bottomrule
  \end{tabular}

>>>>

\begin{table}[!ht]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the selected real-world models.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. For each method, Column "\(|M|\)" denotes the number of minimal trap spaces and Column "time (s)" denotes the computation time in seconds.
    "DNF" means that the method did not finish the computation within one hour.}
  \centering
  \label{tab:result_real}
  \begin{tabular}{lrrrrrrr}
    \toprule
    & & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Proposed method}\\
    \cmidrule(lr){5-6}\cmidrule(lr){7-8}
    model & $n$ & $e$ & $s$ & $|M|$ & time (s) & $|M|$ & time (s) \\ \midrule
    cascade-3~\cite{Tsirvouli2020} & 183 & 603 & 0 & - & - & 1 & 1.65 \\
    CHO-2016~\cite{lee2019signal} & 200 & 696 & 13 & - & - & 1024 & 2.10 \\
    colitis-associated-colon-cancer~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 153 & 1 & - & - & 10 & 0.18 \\
    Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & - & 16 & - & - & 5724 & 0.90 \\
    ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 1100 & 22 & DNF & DNF & DNF & DNF \\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 266 & 75 & - & - & 25600 & 4.54 \\
    Alzheimer~\cite{aghamiri2020automated} & 1169 & - & 469 & - & - & 49152 & 66.17 \\
    cholocystokinin~\cite{aghamiri2020automated} & 404 & - & 95 & - & - & 705024 & 1080.35 \\
    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 557 & 9 & - & - & 375850 & 331.87 \\
    T-cell-check-point~\cite{hernandez2020computational} & 218 & - & 34 & - & - & 15360 & 4.33 \\
    HIV-1-with-T-cell-signaling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & DNF & DNF & 1408 & 1.44 \\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & - & - & 5120 & 0.99 \\
    human-network~\cite{kim2011reduction} & 1953 & - & 675 & DNF & DNF & 2048 & 1770.98 \\
    IL-6-signalling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 86 & 149 & 15 & - & - & 512 & 0.32 \\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 506 & 13 & DNF & DNF & 36852 & 14.19 \\
    inflammatory-bowel-disease~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 287 & 0 & DNF & DNF & 1 & 296.23 \\
    influenza-virus-replication-cycle~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & - & - & 2560 & 1.07 \\
    interferon-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & - & - & 512 & 0.43 \\
    Korkut-2015~\cite{lee2019signal} & 99 & - & 12 & DNF & DNF & 2060 & 2.86 \\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 304 & 72 & - & - & 512 & 3.79 \\
    RA-apoptosis~\cite{aghamiri2020automated} & 431 & - & 59 & DNF & DNF & 640 & 0.70 \\
    adhesion-CIP-migration-cell-cycle~\cite{guberman2020boolean} & 121 & 493 & - & - & - & 78 & 3.72 \\
    KEGG-network~\cite{DBLP:journals/bmcsb/Kwon16} & 1659 & - & 522 & DNF & DNF & 1024 & 1511.07 \\
    signaling-macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 533 & 19 & - & - & 512 & 1.58 \\
    signaling-in-prostate-cancer~\cite{Montagud2021} & 133 & 431 & 0 & - & - & 812 & 1.40 \\
    butanol-production~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 66 & 139 & 13 & - & - & 512 & 0.17 \\
    SN-5~\cite{kim2013rmod} & 2746 & - & 835 & DNF & DNF & 2048 & 3094.04 \\
    TCR-TLR5-signaling-2018~\cite{rodriguez2019cooperation} & 130 & 273 & 2 & - & - & 48 & 0.50 \\
    T-LGL-survival-network-2008~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 61 & 193 & 7 & - & - & 318 & 0.24 \\
    turei-2016~\cite{lee2019signal} & 4691 & - & 1257 & DNF & DNF & DNF & DNF \\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 268 & 25 & - & - & 1024 & 0.67 \\ \bottomrule
  \end{tabular}
